Bioinformatics Assignment 4

### 2016-03-09 bioinformatics/latex/a4.tex
Add a4 stuff.

\section{Problem two: Inter-species RNA duplexes}
We put the 5' human RNA sequences and the 3' Drosophila sequence into a fasta file
and recomputed the duplex energies in the same way as in Problem One:
\textbf{dme-let-7: } $\Delta G = -20.4$\\
\textbf{dme-mir-9a: } $\Delta G = -17.3$\\
\textbf{dme-mir-100: } $\Delta G = -16.5$\\

@@

\section{Problem three: RNA structure commands}
\textbf{a.)} \texttt{cat hsa-mir-100.fa | RNAduplex -T 26}\\
\textbf{b.)} \texttt{ HOW YOU DO DIS??????????????????????}\\

@@

\section{Problem seven: Cuffdiff}

>>>>

\section{Problem two: Inter-species RNA duplexes}
We put the 5' human RNA sequences and the 3' Drosophila sequence into a fasta file
and recomputed the duplex energies in the same way as in Problem One:\\
\textbf{dme-let-7: } $\Delta G = -20.4$\\
\textbf{dme-mir-9a: } $\Delta G = -17.3$\\
\textbf{dme-mir-100: } $\Delta G = -16.5$\\

@@

\section{Problem three: RNA structure commands}
\textbf{a.)} \texttt{cat duplex.fasta | RNAduplex -T 26}\\
\textbf{b.)} \texttt{cat hotair.fasta | RNAfold -T 35}\\

@@

\section{Problem seven: Cuffdiff}
RPKM stands for \textbf{Reads per Kilobase} of gene per length per \textbf{Million}.
This is basically taking the number of reads mapped to a gene over the total number
of reads, which is the ``activity'' of that gene. This number then needs to be corrected
for the length of the transcript, so we divide by the transcript length.\\

FPKM stands for \textbf{Fragments per Kilobase} of gene per length per \textbf{Million}.
This is the exact same as RPKM, except fragments of cDNA are used instead of just reads.
Fragments are better because they take into account things like paired-end effects.\\

\section{Problem eight: Cuffdiff options}

\textbf{a.)} The \texttt{-L/--labels} option can be used to specify the labels used
in the \texttt{cuffdiff} output. This is a comma-separated lsit if multiple labels
are to be used.\\

\textbf{b.)} \texttt{cuffdiff} finds expression levels for transcripts, it doesn't create
a map of transcripts, or transcriptome. \texttt{cufflinks} is the tool to create a
transcriptome assembly.\\

\section{Problem nine: Intersection vs Union}
Here we use the tutorial described in Trapnell 2013 to compute the log fold-change.\\

To compute via the union method, we just count the number of hits over the union of
the exons. We find that there are 25 hits for both Condition A and Condition B, so:

\begin{align*}
  \log_2\left(\frac{25}{25}\right) &= 0\\
\end{align*}

To find via the intersection method, we do the same with the intersection of the two
exons and find there are 19 hits for both Condition A and Condition B, so:

\begin{align*}
  \log_2\left(\frac{19}{19}\right) &= 0\\
\end{align*}

Finally to find the true expression, we count the hits for each exon they belong to
and divide by the exon's length:

\begin{align*}
  \log_2\left(\frac{\frac{14}{3L}+\frac{11}{2L}}{\frac{15}{3L}+\frac{9}{2L}}\right)
  &= \log_2\left(\frac{\frac{28+33}{6L}}{\frac{30+27}{6L}}\right)\\
  &= \log_2\left(\frac{61}{57}\right)\\
  &= 0.098\\
\end{align*}
